---
title: "Multinomial Analysis"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Websites with Multinomial tutorials
 <https://stats.idre.ucla.edu/r/dae/multinomial-logistic-regression/>.
 <https://cran.r-project.org/web/packages/nnet/nnet.pdf/.>
 <https://www.princeton.edu/~otorres/LogitR101.pdf>.
 

## Websites about model selection
<http://www.stat.wisc.edu/~ane/st572/notes/lec05.pdf>.


Based on the calculated p-value, a false rejection of the null hypothesis is
| extremely unlikely. We are confident that fit3 is significantly better than fit1,
| with one caveat: analysis of variance is sensitive to its assumption that model
| residuals are approximately normal. If they are not, we could get a small p-value
| for that reason. It is thus worth testing residuals for normality. The Shapiro-Wilk
| test is quick and easy in R. Normality is its null hypothesis. Use
| shapiro.test(fit3$residuals) to test the residual of fit3.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
